\cvsection{Employment}
\cvevent{Mathematics Course Assistant}{}{Feb 2018 -- present}{Stellenbosch University, ZA}
\smallskip
I have tutored the following undergraduate classes (starred are those I currently teach):
\medskip
\begin{itemize}
\item \makebox[4.1em][l]{\emph{3rd year:}} Algebra$^*$, Fredholm theory
\item \makebox[4.1em][l]{\emph{2nd year:}} Linear algebra$^*$, advanced calculus$^*$, analysis$^*$
\item \makebox[4.1em][l]{\emph{1st year:}} Linear algebra, calculus
\end{itemize}

\divider % Remove if over page boundary

\cvevent{Software Development Engineer Intern}{}{\parbox[c]{15em}{\smallskip Nov 2019 -- Feb 2020\\Dec 2020 -- Feb 2021}}{Amazon Web Services, ZA}
\smallskip
I interned twice for \textit{Amazon Web Services} (AWS) where I worked on \textit{Elastic Compute Cloud} (EC2).

\divider % Remove if over page boundary

\cvevent{Private Tutoring}{}{Aug 2017 -- Mar 2018}{Independent, \emph{ad hoc}}
\smallskip
Grade 11--12 mathematics, both national curriculum \& advanced programme mathematics.


\cvsection{Personal Projects}
\cvproject{Course Enrichment for 2019}
\begin{itemize}
\item I attended an Honours-level course on \textit{Lie theory}, which I applied to Hydrogen-atom physics as part of my 3rd-year abstract mathematics project.
\item I attended a fluid dynamics course in my spare time.
\end{itemize}
\smallskip

\cvproject{\emph{Global Game Jam} \& Other Development}
\begin{itemize}
\item Since 2019, a friend and I have partaken in the annual \href{https://globalgamejam.org/about}{\emph{Global Game Jam}}, wherein participants have 3--5
    days to design \& build a computer game from scratch.
\item Having started with no knowledge in \emph{Unity}, \emph{Godot}, \emph{C\#}, or game design, this was a rapid learning experience.
\item We have independently created several game prototypes since, including a web version of Hive (see my \href{https://github.com/Doormango}{GitHub}).
\end{itemize}
\smallskip

\cvproject{Algebra \& Geometry Investigation}
\begin{itemize}
\item I spent the holiday of 2017--2018 independently working through every page \& exercise of Alan Beardon's wonderful book,
    \href{https://www.cambridge.org/za/universitypress/subjects/mathematics/algebra/algebra-and-geometry}{\emph{Algebra and Geometry}}.
\item As my introduction to abstract mathematics, it now holds a special place in my heart.
\end{itemize}
\smallskip

\cvproject{\emph{Project Euler} Problems}
\begin{itemize}
\item An ongoing project of mine (since 2015) is completing programming challenges from the \href{https://projecteuler.net/about}{\emph{Project Euler}} database.
\item These challenges demand mathematical proficiency \& creativity to solve in the permitted 1min run-time.
\end{itemize}
\smallskip



% \cvsection{Strengths}

% \cvtag{Hard-working (18/24)} 
% \cvtag{Persuasive}
% \cvtag{Motivator \& Leader}
